\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Viliam Ro\v{c}kai, PhD.}

\section{About Me}

I'm a software engineer with broad experience all over the stack. I concentrate on problem-solving and am not afraid of cutting edge technologies. My QA past doesn't let me trust any code before it is thoroughly tested and my academic past makes me enjoy scientific papers, math equations, and rational skepticism. I'm a big fan of open-source and a long-term Linux user.
\\

I specifically care about code readability, documentation and getting things done.
\\

Over the last decade, I was very lucky to be passionate about my jobs and not just do them to earn a living. I would be grateful never have to change this. Life is short, let's do stuff that matters.

\section{Projects}

Visit \href{https://vrockai.github.io/}{vrockai.github.io} to see the full portfolio.

\section{Recent Work experience}

\begin{eventlist}

\item{July 2015 -- Present}
     {DNAstack}
     {Senior Front-End Developer}

Front-end development, deployment and QA. Building of complex SPAs in the domain of genomics. 
Automating the FE/BE deployment. Jenkins installation, administration and maintenance.

\item{2012 -- 2015}
     {Red Hat}
     {Software Developer}

FE (AngularJS) and BE (Java EE) development on several Red Hat projects using mostly Red Hat technologies.

\item{2008 -- 2012}
     {Red Hat}
     {QA Engineer}

QA (automated UI and performance testing) of the JBoss Portal project (later GateIn) and related projects. Covered the whole JBoss Portal project with UI tests (Selenium). Improved the performance of the Picketlink project by tweaking Hibernate settings as a part of performance QA.

\end{eventlist}

\personal
    [vrockai.github.io]
    {Brno, Czech Republic}
    {}
    {viliam.rockai@gmail.com}

\section{Education}

\begin{yearlist}

\item[]{2005 -- 2013}
     {Automatic discovery of concepts in documents written in natural language (PhD.)}
     {Technical University in Kosice, Slovakia}

\item[]{2000 -- 2005}
     {Mining of concepts and semantic relations from texts in natural language (MSc.)}
     {Technical University in Kosice, Slovakia}

\end{yearlist}

\section{Past Work experience}
\begin{eventlist}
\item{2006 - 2008}
     {Acision}
     {Software Developer}

Junior BE developer working on in-house projects based on JBoss Portal. First experience with agile (pair) programming and test driven development.

\item{2005 - 2006}
     {Siemens PSE}
     {Software Developer}
     
Software developer responsible for development and maintenance of an Eigner-PLM product. The product was a very custom piece of technology (similar to SAP) highly reliable on an Oracle DB.
\end{eventlist}
\section{Communication skills}

\begin{factlist}
\item{Slovak}{Native speaker}
\item{English}{Fluent}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Using daily}
     {Angular, TypeScript, JavaScript, Node.js}

\item{Using weekly}
     {Jenkins, Docker, Selenium, Cypress.io}

\item{Using monthly}
	 {Java EE, Maven, AngularJs, Python}

\item{Using annually}
	 {D3.js, React}

\end{factlist}

\end{document}
